scikit-image, a Python library for 2D and 3D image processing

### 2016-08-17 skimage_tomo.tex
Some text for captions + small changes in ecosystem figure

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
 The gallery of examples consists of an array of thumbnails (left part),
 which link to example webpages, each centerered on a specific image
 processing task. Each webpage includes Python code generating a figure,
 the figure itself, as well as a short tutorial explaining the image
 processing operations and the code. \label{fig:ecosystem}}
\end{figure*}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
  should go here. \label{fig:spyder}}
\end{figure*}

>>>>

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
	ecosystem}. Images are opened from files as \texttt{NumPy}
	arrays. Functions of \texttt{scikit-image} transform image arrays
	into other arrays with the same dimensions, or into arrays of
	numbers corresponding to features of the image. The output of
	scikit-image functions can be passed to other Python modules
	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
	\texttt{scikit-learn}. Image-shaped arrays are transformed into
	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
	(3D). A variety of environments is available for code development
	and execution, from classical IDEs to Jupyter notebooks.
    \label{fig:ecosystem}}
\end{figure*}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
    \caption{\csentence{The Spyder IDE} integrates a text editor (with
	syntax highlighting), the IPython interpreter, as well as a panel
	for code introspection (online help, variable explorer, \dots).
 \label{fig:spyder}}
\end{figure*}
